A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-01-24 paper.tex
modify the pipeline pic and the abstract

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast}
\end{abstract}
%

@@

\section{Gestures taxonomies}
By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exists according to the point of view:

@@

* Taxonomy based on the number of strokes used in the gesture.
We use this criteria to distinguish between gestures constructed by only one path and between those using many path, so the recognition needs to wait for all strokes before the recognition

@@

@@

\png{handg}{Family of supported gestures}

Steps for skin-color based gesture detection

\section{Technical Aspects}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}

\subsection{Used Material}
Technical aspects of the camera, and used framerate.

\ignore{
60 Hz, 640x480
}

@@

Naturelness came from the analysis of gestures used in talk shows.
(gesutures used many times means nature gestures)
Reverse thinking.

>>>>

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with intelligent devices.
In this paper we present our work to generate intelligent TVs modules capable of
recognizing human gestures through a low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
Then we present a new gesture library generated after an analysis of TV's Talk-shows.

\ignore{
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
}
\keywords{natural gesture interaction, low-cost gesture recognition, interactive TV broadcast}
\end{abstract}
%

@@

\section{Gestures taxonomies}
By looking in the possible gestures human can generate, we get a huge amount of possibilities so there is a need for a taxonomy. Many possible taxonomies exist according to the point of view:

@@

* Taxonomy based on the number of strokes used in the gesture.
We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition

@@

Nous avons choisi celle-ci, car elle correspond aux besoins que nous avons identifier dans les scenarios d'utilisation de la télé interactive

@@

\png{handg}{Family of supported gestures}
\ignore{
Explanation of the figures

Steps for skin-color based gesture detection
}
\section{Technical Aspects}
Pipeline of the work:
\png{pipeline}{Pipeline of work components}

\subsection{Used Materials}
We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 Frame-per-second.

\ignore{
}

@@

Naturelness came from the analysis of gestures used in talk shows.
(gestures used many times means nature gestures)
Reverse thinking.
